
***Factor*** \
  Answer: one factors which is model\
***Levels of each factor***\
  Answer : 4  levels which Random Forest, Naive Bayes, Support Vector Machines, Linear Discriminant Analysis\
***Experimental unit***\
  Answer : dataset\
***Response. ***\
  Answer : accuracy. \
***Number of Replications.***\   
  Answer : forty-five\
***Experimental Methodology. ***\
Answer:\
 Replication : forty-five times
 Randomization : dataset
 Blocking : proportion of train/test data which are (0.9/0.1, 0.8/0.2, 0.7/0.3) \ 
 \
 

**************************************************************************************************************** \
\
***Experimental Design code in the R code *** \

****************************************************************************************************************
\
**Question2**  \
##RBD\
```{r}
Data<-read.csv("Experiment.csv",header = TRUE) 
Data$Model = factor(Data$Model)
Data$Block= factor(Data$Block)
str(Data)
```
```{r}
library(ggplot2)
p <- ggplot(Data, aes(x=Model, y=Accuracy, group=Model, col = Model)) + geom_point(aes(fill=Model))+ylab("Accuracy")
p + facet_grid(. ~Block) + theme(axis.text.x = element_text(angle = 90))
```
```{r}
aov = aov(data = Data, Accuracy~Model+Block)
summary(aov)

```
**summary**\
Analysis variance indicates that at 5% level of significance there is sufficient evidence(F(3,713) = 22120.060, P= <2e-16) to conclude that the average number of accuracy for each model are not equal.\
\
\
```{r}
plot(aov)
```
\
##Histrogram
```{r}
hist(residuals(aov))
```
\
##Tukey HSD\
```{r}
#install.packages("agricolae")
```
\
```{r}
library(agricolae)
#Tukey's Studentized range test
Tukey=HSD.test(aov,"Model");
Tukey
```
\
```{r}
TukeyHSD(aov)
```
\
```{r}
plot(Tukey)
```
\
```{r}
tapply(Data$Accuracy,Data$Model,mean)
```
\
**summary**
Across methods average accuracy in Random Forest, Naive Bayes, Support Vector Machines, Linear Discriminant Analysis are pairwise are different. The average accuracy for Random Forest is highest. 
\
\
\
*******************************************************************************************************












